\documentclass[14pt]{exam}
\usepackage{amsmath,amssymb}
\title{\underline{\textbf{MATHEMATICS}}}
\author{SECTION-A}
\date{}

\begin{document}
\maketitle
\begin{questions}
	\question Write the principal value of $\tan^{-1} (1)+\cos^{-1} (-\frac{1}{2})$.

	\question Write the value of $\tan \biggl(2 \tan^{-1} \frac{1}{5} \biggl)$

	\question Find the value of a if $\begin{bmatrix}
		a-b & 2a+c\\
		2a-b & 3c+d
	\end{bmatrix}
	=
	\begin{bmatrix}
		-1 & 5\\
		0 & 13
	\end{bmatrix}$

	\question If $\begin{vmatrix}
		x+1 & x-1\\
		x-3 & x+2
	\end{vmatrix}
	=
	\begin{vmatrix}
		4 & -1\\
		1 & 3
	\end{vmatrix}$, then write the value of $x$.

	\question If $\begin{bmatrix}
		9 & -1 & 4\\
		-2 & 1 & 3
	\end{bmatrix}
	=A+ \begin{bmatrix}
		1 & 2 & -1\\
		0 & 4 & 9
	\end{bmatrix}$, then find the matrix $A$.

	\question Write the degree of the differential equation $x^3 \biggl(\frac{d^2y}{dx^2} \biggl)^2+x \biggl(\frac{dy}{dx} \biggl)^4=0$.

	\question If $\vec{a}=x\hat{i}+2\hat{j}-z\hat{k}$ and $\vec{b}=3\hat{i}-y\hat{j}+\hat{k}$ are two equal vectors, then write the value\\ of $x+y+z$.
	
	\question If a unit vector $\vec{a}$ makes angles $\frac{\pi}{3}$ with $\hat{i}$, $\frac{\pi}{4}$ with $\hat{j}$ and an acute angle $\theta$ with $\hat{k}$, then find\\ the value of $\theta$.

	\question Find the Cartesian equation of the line which passes through the point $(-2,4,-5)$ and\\ is parallel to the line $\frac{x+3}{3}=\frac{4-y}{5}=\frac{z+8}{6}$.

        \question The amount of pollution content added in air in the city due to $x$-diesel vehicles is given\\ by $P(x)=0.005x^3+0.02x^2+30x$. Find the marginal increase in pollution content when\\ 3 diesel vehicles are added and write which value is indicated in the above question.\\

	\centerline{SECTION-B}

	\question Show that the function f in $A=\mathbb{R}-\bigl\{\frac{2}{3}\bigl\}$ defined as $f(x)=\frac{4x+3}{6x-4}$ is one-one and onto.Hence\\ find $f^{-1}$.

	\question Find the value of the following:\\ tan$\frac{1}{2}\biggl[$sin$^{-1}\frac{2x}{1+x^{2}}+$cos$^{-1}\frac{1-y^2}{1+y^2}\biggl], |x|<1,y>0$ and $xy>1$.

	\question Prove that: tan$^{-1}\bigl(\frac{1}{2}\bigl)$+tan$^{-1}\bigl(\frac{1}{5}\bigl)$+tan$^{-1}\bigl(\frac{1}{8}\bigl)=\frac{\pi}{4}$

	\question Using properties of determinants, prove the following:\\ $\begin{vmatrix}
		1 & x & x^2\\
		x^2 & 1 & x\\
		x & x^2 & 1
	        \end{vmatrix}
		=(1-x^3)^2.$

	\question Differentiate the following function with respect to $x$:\\
	$(\log x)^x+x^{\log x}$

	\question If $y=\log\biggl[ x+\sqrt{x^2+a^2} \biggl]$, show that $(x^2+a^2)\frac{d^2y}{dx^2}+x\frac{dy}{dx}=0.$

	\question Show that the function $f(x)=|x-3|, x\in\mathbb{R}$, is continuous but not differentiable at $x=3$.

	\question If $x=a \sin t$ and $y=a(\cos t+\log \tan\frac{t}{2})$, find $\frac{d^2y}{dx^2}.$

	\question Evaluate: $\int \frac{\sin(x-a)}{\sin(x+a)} dx$

	\question Evaluate: $\int \frac{5x-2}{1+2x+3x^2} dx$

	\question Evaluate: $\int \frac{x^2}{(x^2+4)(x^2+9)} dx$

	\question Evaluate: $\int_0^4 (|x|+|x-2|+|x-4|) dx$

	\question If $\vec{a}$ and $\vec{b}$ are two vectos such that $|\vec{a}+\vec{b}|=|\vec{a}|$, then prove that $2\vec{a}+\vec{b}$ is\\ perpendicular to $\vec{b}$.

	\question Find the coordinates of the point, where the line $\frac{x-2}{3}=\frac{y+1}{4}=\frac{z-2}{2}$ intersects the\\ plane $x-y+z-5=0$. Also find the angle between the line and the plane.

	\question Find the vector equation of the plane which contains the line of intersection of the\\ planes $\vec{r} \cdot (\hat{i}+2\hat{j}+3\hat{k})-4=0$ and $\vec{r} \cdot (2\hat{i}+\hat{j}-\hat{k})+5=0$ and which is perpendicular\\ to the plane $\vec{r} \cdot (5\hat{i}+3\hat{j}-6\hat{k})+8=0$.

	\question A speaks truth in $60\%$ of the cases, while B in $90\%$ of the cases. In what percent of\\ cases are they likely to contradict each other in stating the same fact$?$ In the cases of\\ contradiction do you think, the statement of B will carry more weight as he speaks\\ truth in more number of cases than A$?$\\

	\centerline{SECTION-C}

	\question A school wants to award its students for the values of Honesty, Regularity and Hard\\ work with a total cash award of $\$6,000$. Three times the award money for Hardwork\\ added to that given for honesty amounts to $\$11,000$. The award money given for\\ Honesty and Hard work together is double the one given for Regularity. Represent the\\ above situation algebraically and find the award money for each value, using matrix\\ method. Apart from these values, namely, Honesty, Regularity and Hard work, suggest\\ one more value which the school must include for awards.

	\question Show that the height of the cylinder of maximum volume, that can be inscribed in a\\ sphere of radius R is $\frac{2R}{\sqrt{3}}$. Also find the maximum volume.

	\question Find the equation of the normal at a point on the curve $x^2=4y$ which passes through\\ the point $(1,2)$. Also find the equation of the corresponding tangent.

	\question Using integration, find the area bounded by the curve $x^2=4y$ and the line $x=4y-2$.

	\question Using integration, find the area of the region enclosed between the two circles\\ $x^{2}+y^{2}=4$ and $(x-2)^{2}+y^{2}=4$.

	\question Show that the differential equation $2ye^{\frac{x}{y}}dx+(y-2x~e^{\frac{x}{y}})dy=0$ is homogeneous. Find the particular solution of this differential equation, given that $x=0$ when $y=1$.

	\question Find the vector equation of the plane passing through three points with position\\ vectors $\hat{i}+\hat{j}-2\hat{k},2\hat{i}-\hat{j}+\hat{k}$ and $\hat{i}+2\hat{j}+\hat{k}$. Also find the coordinates of the point of\\ intersection of this plane and the line $\vec{r}=3\hat{i}-\hat{j}-\hat{k}+\lambda(2\hat{i}-2\hat{j}+\hat{k})$.

	\question A cooperative society of farmers has $50$ hectares of land to grow two crops A and B.\\ The profits from crops A and B per hectare are estimated as $10,500$ and $9,000$\\ respectively. To control weeds, a liquid herbicide has to be used for crops A and B at\\ the rate of $20$ litres and $10$ litres per hectare, respectively. Further not more than $800$\\ litres of herbicide should be used in order to protect fish and wildlife using a pond\\ which collects drainage from this land. Keeping in mind that the protection of fish and\\ other wildlife is more important than earning profit, how much land should be\\ allocated to each crop so as to maximize the total profit$?$ Form an LPP from the above\\ and solve it graphically. Do you agree with the message that the protection of wildlife\\ is utmost necessary to preserve the balance in environment $?$

	\question Assume that the chances of a patient having a heart attack is 40$\%$. Assuming that a\\ meditation and yoga course reduces the risk of heart attack by 30$\%$ and prescription of\\ certain drug reduces its chance by 25$\%$. At a time a patient can choose any one of the\\ two options with equal probabilities. It is given that after going through one of the two\\ options, the patient selected at random suffers a heart attack. Find the probability that\\ the patient followed a course of meditation and yoga. Interpret the result and state\\ which of the above stated methods is more beneficial for the patient.

\end{questions}
\end{document}
